Textmining in Economics

### 2017-12-08 paper/doc/doc2.tex
new

\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
			style=authoryear-comp,
			isbn=false,
			doi=false,
			bibstyle=authoryear,
			natbib,
			]{biblatex}
\usepackage{eurosym}
\usepackage{enumitem}
\usepackage{url}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{amsmath}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{multirow,rotating}
\usepackage[autostyle]{csquotes}
\usepackage[toc,page]{appendix}
\usepackage{lscape}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{eurosym}

@@

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares.

@@

Media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers. The demand on both consumer-sides are often linked via indirect network externalities. The market in which media outlets operate are accordingly referred to as two-sided or multi-sided markets. The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}. The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}. However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.

Online news are typical examples of two-sided markets where the news pages can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising.

Depending on the strength of the indirect network effects, publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}. Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to to obtain access to the viewers. Many online news agencies also provide a part of their editorial content as a premium service. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only function if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many readers as possible to their platform, and thus exploit the indirect network effects on the advertising site. % What is the share of advertising revenue in total earnings of german online newspaper ?

In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time. Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher.

@@

We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g. the author or date of a document). STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012} and \citet{grimmer_text_2013} for an overview.}

The basic topic model has been extended in variety of ways. \citet{blei_dynamic_2006} considers documents that are indexed by publication date date and allows the topics to evolve in time. To relax the assumption that all texts in the modeled corpus are generated by the same underlying process, \cite{roberts_model_2016} introduces the structural topic model (STM), that provides a way to include covariates. Using a generalized linear model on document-level metadata allows the researcher to link topics to covariate data and to model changes in topic prevalence over time.

@@

We conduct our estimation on a sample of 10531 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 28.10.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles of six mainstream german online news portals\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} using the the Event Regestry API.\footnote{For more information see http://eventregistry.org/documentation. The scraping code was written in Python and can be made available on request.} We then filter those articles that contain the term "Bundestagswahl" (Federal Election) in their text body. We use the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}

Figure \ref{fig_distr1} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th. Most of the articles are published by welt.de, followed by stern.de (see \ref{fig_distr2}).

\begin{figure}[H]
	\caption{Article distribution...}
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/timeline.png}
			\caption{...by date \& news source}
			\label{fig_distr1}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/bar.png}
			\caption{... by news source}
			\label{fig_distr2}
		\end{subfigure}
	\end{center}
\end{figure}

\begin{figure}[H]
	\caption{Distribution of Facebook shares...}
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/fb_shares.png}
			\caption{...by date \& news source}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth]{../figs/fb_shares_mean.png}
			\caption{... by news source (mean)}
		\end{subfigure}
	\end{center}
	\label{fig_fb_shares}
\end{figure}

@@

% ------------------
% Text Pre-Procesing
% ------------------
\subsection{Text pre-procesing}

@@

% ----------------------
% Structural topic Model
% ----------------------
\section{Topic detection}\label{ch_model}

The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citept{roberts_stm:_2016}. The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:

@@

The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm available in R's stm package \citep{roberts_stm:_2016}. Regularizing prior distributions are used for $\gamma$, $\kappa$ and (optionally) $\Sigma$. To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.

% ----------------------
% Model Selection
% ----------------------
\subsection{Model selection}

Topic models are generally inaccurate, since the number of topics must be determined a priori. Furthermore, multiple solutions exist for the optimization problem. Ex post analysis of several model specifications helps to evaluate its quality, as well as the number of topics and metadata selected.

The most common choice is the probability of held-out documents \citep{grimmer_bayesian_2010}. Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}. Another strategy to find an appropriate number of topics is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}. Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}. We run multiple model specifications and compare them based on held-out likelihood estimation, residual checks as well as semantic coherence to chose the number of topics that best fits the corpus to be 50. Furthermore, we use the source of each article (the media house) and the month it was published as a covariates in the topic prevalence portion of the model. In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published.

% ----------------------
% Evaluation
% ----------------------
\subsection{Evaluation}

The most effective method for assessing model fit is to carefully read documents that are closely associated with particular topics to verify that the semantic concept covered by the topic is reflected in the text. The parameter θd provides an estimate of each document’s association with every topicmaking it straightforward to effectively direct analyst engagement with the texts (see, e.g., Roberts, Stewart, and Tingley 2014a). An overview of manual validation procedures can be found in Grimmer and Stewart (2013).\cite{roberts_model_2016}

To validate the accuracy with which the fitted model is capturing the content of a document, we first conduct a process of informal manual audits \citep{gentzkow_text_2017}: We inspect inspect a subset of documents alongside the fitted topics to cross-check against the coding a human would produce by hand. Figure \ref{fig_classification} shows sample documents classified to each topic for reference. We produce a random sample of 7 posts from the 300 highest probability fits per topic.

\begin{figure}[H]
\centering
	\caption{Sample articles}
	\includegraphics[width=\textwidth]{../figs/topic-classification-sample.png}	
	\label{fig_classification}
\end{figure}

The interpretability or semantic coherence of topics can vary considerably. \citet{mimno_optimizing_2011} propose a topic semantic coherence score computed from in-corpus word co-occurrence statistics, and show strong agreement with human evaluations.

\cite{mimno_optimizing_2011}
The evaluation of statistical topic models has traditionally been dominated by either extrinsic methods (i.e., using the inferred topics to perform some external task such as information retrieval \citep{wei_lda-based_2006} or quantitative intrinsic methods, such as computing the probability of held-out documents \citep{wallach_evaluation_2009}. Recent work has focused on evaluation of topics as semantically coherent concepts. For example, \citet{chang_reading_2009} found that the probability of held-out documents is not always a good predictor of human judgments.

After performing the topic modeling, we can generate an overview of the news landscape about the german elections. Each group is composed of the most relevant words for that topic, and a manually-determined label. The distances that the topics have from each other reflect their semantic distance, or basically how different the words are for that topic. It is computed as the Jensen-Shannon divergence between each of the topics according to the differences in their word-topic probabilities. We then apply principal coordinates analysis in order to project the distance matrix down to two dimensions.

%\begin{figure}[H]
%\centering
%	\caption{News Landscape}
%	\includegraphics[width=\textwidth]{../figs/news-landscape-map.png}	
%	\label{fig_landscape}
%\end{figure}

%
%\begin{figure}[H]
%\centering
%	\caption{Sum of Facebook shares by topic}
%	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
%	\label{fig_fb_shares_topic}
%\end{figure}

\section{Regression}\label{ch_regression}

The examination of the topic probability distribution revealed that most documents are assigned a unique topic with high probability (65\% and higher), so that we can classify each document based on which topic has the highest probability. We keep only those documents, where the posterior probability of this topic is greater than 0.6 which left us with 6240 documents.

The proportion of zeros in the independent variable (number of Facebook shares) is about 66\%. One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$. In this model zero counts can come from either population, while positive counts come only from the second one.

The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group. A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.

The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process. The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1.

If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities.

\begin{align*}
	g(y)=\begin{cases}
		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
		(1-f_1(0))f_2(y) if y\geq 1
	\end{cases}
\end{align*}

The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.

>>>>

\documentclass[12pt,a4paper,notitlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[backend=biber,
			style=authoryear-comp,
			isbn=false,
			doi=false,
			bibstyle=authoryear,
			natbib,
			]{biblatex}
\usepackage{eurosym}
\usepackage{enumitem}
\usepackage{url}
\usepackage{blindtext}
\usepackage{hyperref}
\usepackage{breakurl}
\usepackage{amsmath}
\usepackage{titling}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{pgfplots}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{dcolumn}
\usepackage{tikz-3dplot}
\usepackage{subcaption}
\usepackage{float}
\usepackage{adjustbox}
\usepackage{multirow,rotating}
\usepackage[autostyle]{csquotes}
\usepackage[toc,page]{appendix}
\usepackage{lscape}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{bm}
\usepackage{eurosym}
\usepackage{pdflscape}

@@

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares. We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de. They are all providers of online news, whereby Tagesschau.de is the only publicly funded service. The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.

@@

Media outlets naturally appear as two-sided platforms, that allow interaction between two categories of consumers: audiences and advertisers. As the demand on both consumer-sides are linked via indirect network externalities, the market in which media outlets operate are referred to as two-sided or multi-sided markets. The theoretical literature on two-sided markets originates from the analysis of credit card markets \citep{rochet_platform_2003} and was later transferred to the concept of other industries, such as dating agencies, real estate agents, and internet “business-to-business” websites \citep{caillaud_chicken_2003}. The basic concept of two-sided markets was already discussed decades ago in several economic studies, especially on media markets \citep{corden_maximisation_1952}, \citep{gustafsson_circulation_1978}, \citep{blair_pricing_1993}. However, comprehensive analyses have only been carried out in the last ten years, starting with the works of \citet{rochet_platform_2003}, \citet{evans_empirical_2003} and \citet{armstrong_competition_2006}.

Advertising-supported media such as online newspapers are typical examples of two-sided markets where the newspaper can be conceived as platforms that allow interaction between audiences ("eyeballs") and advertisers. The newspaper creates (or buys) content to attract viewers which in turn attract advertisers who pay for readers' attention.\cite{evans_industrial_2005} The size and characteristics of the audience has a positive effect on the advertisers' willingness to pay, as advertisements are typically sold based on cost per viewer, often expressed in terms of the cost of reaching a thousand viewers (CPM). Advertising can also have an effect on the recipients, which can be both negative and positive, depending on the quality of the advertising. Depending on the strength of the indirect network effects, private publisher maximize their revenue by balancing the demand from advertisers and subscribers using different business models \citep{evans_economics_2008}.\footnote{Public media such as Tagesschau.de do not depend on revenues from the advertising industry, which means that there is no two-way market structure.} Many traditional newspapers follow the subscription/advertising model, where the publisher charges both market sides: The audience pays a fee to obtain access to the content, and advertisers pay to obtain access to the viewers. Many online news agencies provide part of their editorial content for free and hide another, more exclusive part behind a paywall. However, since the Internet has considerably simplified the possibilities for obtaining information and thus reduced the marginal utility of content, such a business model can only be efficient if the content is very exclusive. As a result, many publishers rely on a free-media model, in which the publishers do not charge viewers for access to the media at all, in order to attract as many eyeballs as possible to their platform, and thus exploit the indirect network effects on the advertising site. In fact, most advertising-financed online magazines earn their gross margin from advertising.\cite{evans_industrial_2005} In order to maximize their profits, these companies have an interest in attracting as many readers as possible. Facebook is an important traffic supplier for news sites: Over 487.000 news articles from TOP15\footnote{Bild.de, bunte, Chip, FAZ, Focus, Handelsblatt, Heise, N-TV, Spiegel, Sport1, Stern, Süddeutsche, Tagesschau, Welt, Zeit} media were shared 123.000.000 times on Facebook (94\%), Twitter(3.5\%) and Google+(2.3\%).\cite{schiller_development_2016} In addition to the quantity of the audience, the demographic characteristics of recipients also have an influence on the willingness to pay on the advertiser site. Online advertising makes it possible to target ads to particular consumers in real time. Facebook instant articles facilitates this targeting, as they make the public users profile data available to the publisher. However, not all topics are equally often distributed in social media. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, while sports news is more likely to be shared from Bild.de.

While these pre-defined resorts give an indication on the content of an article, multiple articles in the same resort probably don't cover the same topics. Especially if the articles originate from different news portals. Furthermore, articles can contain more than one topic. We use a structural topic model to reveal the underlying topics of a collection of articles, and how the articles exhibit them. We then estimate the effect of topic prevalence on the number of Facebook shares. We use a data set of online news articles about domestic politics dated from 01.06.2017 to 22.11.2017\footnote{German federal elections took place on 24th of September 2017.} from seven German content providers: Bild.de, Die Welt, Focus Online, Spiegel Online, Stern.de, Zeit Online and Tagesschau.de. They are all providers of online news, whereby Tagesschau.de is the only publicly funded service. The latter was also included in the study to verify whether the topics differ when the content is created on the basis of a different business model.

Figure \ref{fig_uuser} shows the coverage of the six private online news provider for the period June to November 2017 in terms of unique user.\footnote{The Term unique user refers to the number of different internet users who have visited the website within a certain period of time. The unique user is the basis for the calculation of coverage and structures of online advertising media as well as essential factors for media planning.} It is striking that Bild.de has the greatest reach over the entire course of time, except on election day and one day after. Here, DIE WELT (+123\%), FOCUS ONLINE (+71\%) and SPIEGEL ONLINE (+57\%) in particular are making a big leap. SPIEGEL ONLINE overtakes Bild.de (+21\%) on the day after the elections (25.09.2017). ZEIT ONLINE and stern.de have a comparatively small coverage. Yet here too, there is a short-term increase in the range of coverage during the elections (+44\% for stern.de and +81\%  for ZEIT ONLINE).

 % What is the share of advertising revenue in total earnings of german online newspaper ?

\begin{figure}[H]
	\caption{Unique User in Million}
	\begin{center}
			\includegraphics[width=.9\textwidth]{../figs/uniqueUser.png}
			\label{fig_uuser}
	\end{center}
\end{figure}

@@

We use the structural topic model (STM) developed by \citet{roberts_model_2016} that allows us to incorporate document specific covariates (e.g. the author or date of a document). STM is a recent extension of the standard topic modeling technique, labeled as "latent Dirichlet allocation" (LDA), which refers to the Bayesian model in \citet{blei_latent_2003} that treats each word in a topic and each topic in a document as generated from a Dirichlet - distributed prior.\footnote{See also \citet{griffiths_probabilistic_2002}, \citet{griffiths_finding_2004} and \citet{hofmann_probabilistic_1999}. \citet{pritchard_inference_2000} introduced the same model in genetics for factorizing gene expression as a function of latent populations.} Topic models formalize the idea that documents are formed by hidden variables (topics) that generate correlations among observed terms. Since its introduction into text analysis, LDA has become hugely popular and especially useful in political science.\footnote{see \citet{blei_probabilistic_2012}, \citet{grimmer_text_2013} and \citet{wiedmann_text_2016} for an overview in social science and \citet{gentzkow_text_2017} give an overview of text mining applications in economics.} \citet{wiedmann_text_2016} use topic model methods in on large amounts of news articles from two german newspapers published between 1959 and 2011, to reveal how democratic demarcation was performed in Germany over the past six decades.

@@

We conduct our estimation on a sample of 10531 online news articles from seven news provider about domestic politics dated from 01.06.2017 to 22.11.2017.\footnote{German federal elections took place on 24th of September 2017.} We first extract all online articles of six mainstream german online news portals\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de, Tagesschau.de} using the the Event Regestry API.\footnote{For more information see http://eventregistry.org/documentation. The scraping code was written in Python and can be made available on request.} We then filtered all articles from the section "domestic policy" by checking the URL structure. We used the URL of these articles, to check how many times they where shared on Facebook using the \textit{sharedcount} API.\footnote{http://docs.sharedcount.com/} The returned share count is the sum of (1) the number of likes of this URL, (2) the number of shares of this URL (including copy-pasting a link back to Facebook), (3) the number of likes and comments on stories on Facebook about this URL and (4) the number of inbox messages containing this URL as an attachment.\footnote{See https://developers.facebook.com/docs/graph-api for more information about the Facebook Graph API.}

Figure \ref{fig_distr1}\footnote{The first vertical line indicate the date of the federal elections (24.09.2017), and the second line indicate the date on which the "Jamaika" parties (Union, FDP, Die Grünen) announced the failure of the coalition negotiations (20.11.2017).} shows the distribution of the number of articles from the respective news sources by date. There is a high peak around the federal elections on September, 24th. Most of the articles are published by welt.de, followed by stern.de (see \ref{fig_distr2}).

\begin{figure}[H]
	\caption{Article distribution...}
	\begin{center}
		\begin{subfigure}[normla]{0.8\textwidth}
			\includegraphics[width=\textwidth]{../figs/timeline.png}
			\caption{...by date \& news source}
			\label{fig_distr1}
		\end{subfigure}
		\begin{subfigure}[normla]{0.8\textwidth}
			\includegraphics[width=\textwidth]{../figs/bar.png}
			\caption{... by news source}
			\label{fig_distr2}
		\end{subfigure}
	\end{center}
\end{figure}

% ------------------
% Text Pre-Procesing
% ------------------

@@

@@

% ----------------------
% Structural topic Model
% ----------------------
\section{Topic detection using the structural topic model}\label{ch_model}

The following description of the generative model of the STM is based on \citet{roberts_structural_2013} and \citet{roberts_stm:_2016}. The process of filling a word-position in a document begins with the generation of a document-specific topic-prevalence vector $d(\boldsymbol{\theta}_d)$ drawn from a logistic-normal distribution, where the parameters are a function of the covariate values:

@@

% ----------------------
% Model Selection
% ----------------------
\subsection{Model and parameter selection}

Topic models are usually imprecise as a number of assumptions have to be made that influence the performance of the classification task. Furthermore, multiple solutions exist for the optimization problem. The STM maximizes the posterior likelihood that the observed data were generated by the above data-generating process using an iterative approximation-based variational expectation-maximization algorithm\footnote{A technical description of this maximization process can be found in \citet{roberts_model_2016}} available in R's stm package \citep{roberts_stm:_2016}. Regularizing prior distributions are used for $\gamma$, $\kappa$ and $\Sigma$. Since an ex ante valuation of a model is hardly possible, we compute a variety of different models with different parameters and compare them with respect to the research problem \citep{gentzkow_text_2017}. To evaluate the accuracy of a model its perplexity can be computed. Similar to cross-validation (VC), different model specifications are compared to how well they do in predicting words within a document \citep{asuncion_smoothing_2012}, \citep{wallach_evaluation_2009}. However, \citet{chang_reading_2009} have proven with large user studies that optimal held out likelihood does not correspond to human perception of semantic coherence of topics. \cite{mimno_optimizing_2011} introduced a measure of coherence of a topic by observing co-occurences of the top $N$ terms of each topic on a document. Another strategy for selecting an appropriate model is to check for residual overdispersion of the variance of the multinomial within the data generating process of the model \citep{taddy_estimation_2012}. Other approaches can be found in \citet{airoldi_reconceptualizing_2010} and \citet{teh_hierarchical_2006}. However, cross-checking some subset of assigned topic distributions to evaluate whether the estimates align with the concept of interest \citep{gentzkow_text_2017}. We apply these manual audits together with numeric optimization based on the topic coherence measure suggested by \citet{mimno_optimizing_2011}.

This process revealed that a model with 25 topics best reflects the structure in the corpus. Furthermore, we use the source of each article (the media house) and the month it was published as covariates in the topic prevalence portion of the model. In other words, the probability distribution of topics depends on the editorial strategy of a media house as well as on the month the article was published. To address problems due to non-convexity, we rely on the spectral initialization approach advocated by \citet{roberts_navigating_2016}.

% ----------------------
% Model Results
% ----------------------
\subsection{Visualize model results}

To get a first overview of the semantic concept of the topics, we produce a random sample of posts with a comparatively high posterior probability for that topic (see \ref{fig_classification}). Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus. To assign a label to each topic, we used a combination of most frequent words in that topic and words with the highest "score", computed as the log frequency of the word in the topic divided by the log frequency of the word in other topics \citep{roberts_stm:_2016}. The most common topic (3) is a general topic full of words that are frequently used in policy news, and therefore is not very interpretable. However, the remaining labels seem to classify a certain topic.

\begin{figure}[H]
	\begin{center}
	\includegraphics[width=0.8\textwidth,keepaspectratio]{../figs/topic_proportion.png}
	\caption{Expected Topic Proportion}
	\label{fig_topic_proportion}
	\end{center}
\end{figure}

%\begin{landscape}
%\begin{figure}[H]
%\centering
%	\caption{Sample articles}
%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
%	\label{fig_classification}
%\end{figure}
%\end{landscape}

% ----------------------
% Effect of covariates
% ----------------------
Since we included news source as a covariate in estimating topical prevalence part within the model, we can estimate the frequency a topic is discussed within a news corpus \citep{roberts_model_2016}. We estimate the conditional expectation of topic prevalence for given document characteristics. More specifically, we estimate a linear model, where the documents are observations, the dependent variable is the posterior probability of a topic and the covariates are the metadata of documents. The stm-package provides a function that uses the method of composition to incorporates uncertainty in the dependent variable, drawing a set of topic proportions from the variational posterior repeated times and compute the coefficients as the average over all results.

Figure \ref{fig_estimateEffects_small} displays topics, where the most significant differences between the news sources are discernible.\footnote{An overview of all estimated topics can be found in the appendix \ref{fig_estimateEffects_full1} and \ref{fig_estimateEffects_full2}.} Topic 2, classifying articles about the diesel scandal, the glpyphosate decision and green policies, occur comparatively more often in tagesschau.de and bild.de, whereas tagesschau.de reports comparatively little about the riots during the G20 summit (topic 9). Topics 10 (about public (financial) statistics) and 13 (about the federal migration office (BAMF), asylum procedures and other issues related to refugees) also seems to be represented comparatively frequently in the tagesschau.de corpus, the latter topic is most often discussed in the DIE WELT corpus. However, topic 20 (the public debate between Die Grünen and FDP in the process of coalition negotiations) is represented significantly more often in the corpus of spiegel.de and bild.de. Topic 26, which classifies articles that deal with terrorism, mainly about the NSU trial and the main defendant Zschäpe as well es IS, is significantly more often present in the corpus of FOCUS ONLINE.

\begin{figure}[H]
	\caption{Mean prevalence of topics within each news source corpus}
	\begin{center}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect2.png}
		\end{subfigure}
		\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect9.png}
		\end{subfigure}
				\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect11.png}
		\end{subfigure}
				\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect13.png}
		\end{subfigure}
				\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect20.png}
		\end{subfigure}
				\begin{subfigure}[normla]{0.3\textwidth}
			\includegraphics[width=\textwidth]{../figs/estimate_effect26.png}
		\end{subfigure}
	\end{center}
	\label{fig_estimateEffects_small}
\end{figure}

Another interesting aspect is how the news sources discusses the different topics, that is, describe the same event with different vocabulary.

% ----------------------
% Regression
% ----------------------
\section{Causal relationship between topics and social media shares.}\label{ch_regression}

%\begin{figure}[H]
%\centering
%	\caption{Sum of Facebook shares by topic}
%	\includegraphics[width=\textwidth]{../figs/fb_shares_topics.png}	
%	\label{fig_fb_shares_topic}
%\end{figure}

In order to answer the primary question of this paper, which topics are more often shared in social networks, we assign a single topic to each article. The examination of the topic probability distribution revealed that most documents are assigned a unique topic with a probability of 50\% and higher (see figure \ref{fig_gamma}), so that we can classify each document based on which topic has the highest probability. We keep only those documents, where the posterior probability of this topic is greater or equal than 0.5 which left us with 6565 documents. Figure \ref{fig_topic_timeline} shows the amount of articles to which a certain topic has been assigned over time. Some of the topics exhibit distinct peaks in the timeline. Topics 11 and 14 deal with the elections, although topic 11 tends to be more about incidents related to the AfD. This graph also illustrates the difference between topic 6 and 17, which have similar labels: topic 6 classifies articles before the negotiations for a "Jamaika" coalition failed, while topic 17 describes the articles written after failure. The highest peak can be found for topic 9, which classifies articles to the riots during the G20 summit. It becomes apparent that more articles deal with riots than with the political content of the summit (topic 8).

The proportion of zeros in the independent variable (number of Facebook shares) is about 15\%. Figure \ref{fig_fb_shares} reveals that within the bin of 0-1 facebook shares, nearly all articles are published by stern.de.

\begin{figure}[H]
	\caption{}
	\begin{center}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/gamma_dist.png}
			\caption{Density of Top-Topics posterior probability}
			\label{fig_gamma}
		\end{subfigure}
		\begin{subfigure}[normla]{0.49\textwidth}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/facebook_shares.png}
			\caption{Grouped Facebook Shares}
			\label{fig_fb_shares}
		\end{subfigure}
		\begin{subfigure}[normla]{0.9\textwidth}
			\includegraphics[width=\textwidth,keepaspectratio]{../figs/topic-timeline.png}
			\caption{Topic Timeline}
			\label{fig_topic_timeline}
		\end{subfigure}
	\end{center}
\end{figure}

Model:

\begin{align*}
	log(FBshares) =\alpha+\beta_{topic}+\beta_{site}+\beta_{textlength}+\epsilon 
\end{align*}

\include{lm1}
%
%One way to model this type of situation is to assume that the data come from a mixture of two populations, one where the counts is always zero, and another where the count has a Poisson distribution with mean $\mu$. In this model zero counts can come from either population, while positive counts come only from the second one. 
%
%The distribution of the outcome can then be modeled in terms of two parameters, $\pi$ the probability of 'always zero', and $\mu$, the mean number of publications for those not in the 'always zero' group. A natural way to introduce covariates is to model the logit of the probability $\pi$ of always zero and the log of the mean $\mu$ for those not in the always zero class.
%
%The two-part model relaxes the assumption that the zeros (whether or not the article is shared) and positives (how often it is shared) come from the same data generating process. The zero-inflated model lets the zeros occur in two different ways: as a realization of the binary process (z=0) and as a realization of the count process when the binary variable z=1. 
%
%If the process generating the zeros is $f_1(.)$ and the process generating the positive responses is $f_2(.)$ then the two-part hurdle model is defined by the following probabilities. 
%
%\begin{align*}
%	g(y)=\begin{cases}
%		f_1(0) + 1(f_i(0))f_2(0) if y=0 \\
%		(1-f_1(0))f_2(y) if y\geq 1
%	\end{cases}
%\end{align*}
%
%The model for the zero versus positive responses is a binary model with the specified distribution, but we usually estimate it with the probit/logit model.

% ----------------------
% Appendix
% ----------------------
\section*{Appendix}
